Parsing Postfix Log Files

### 2009-04-29 doc/logparser-results.tex
Changes made to improve appearance after switching to one-and-a-half spacing.

Efficiency is an obvious concern when the parser routinely needs to parse
large log files.  The mail server that generated the \numberOFlogFILES{}
log files used in this chapter is a production mail server handling mail
for a university department; the benefit of using this mail server is that
its log files exhibit the idiosyncrasies and peculiarities that a mail
server in the wild must deal with, but the downside is that significantly
altering its Postfix configuration to accommodate this project is not an
option.  \Graphref{Mails received per day} and \tableref{Number of mails
received per day: statistics} show that, as expected, it accepts far more
mails on weekdays than at weekends.  Note that mail generated on the server
(e.g.\ bounce notifications, mail re-injected for forwarding, mail sent
from mailing lists) does not contribute to these figures: in particular,
the vast amounts of mail resulting from the mail loops noticeable in later
graphs are not reflected in these figures.

@@

When generating the timing data used in this section, \numberOFlogFILES{}
log files were used, each containing one day's log lines; the three months
of contiguous log files contain \numberOFlogLINEShuman{} log lines and
total \input{build/include-total-size-of-93-log-files}.  Each log file was
parsed 10 times, and the mean parsing time calculated for each log file.
The computer used for test runs was a Dell Optiplex 745, shown in
\tableref{Details of the computer used to generate statistics}; it was
dedicated to the task of gathering statistics from test runs, and did not
run any other programs while test runs were in progress.  Saving results to
the database was disabled for the test runs, because that dominates the run
time of the parser, and the tests are aimed at measuring the speed of
\parsername{} rather than the speed of the database and the disks it is
stored on.  Parsing all \numberOFlogFILES{} log files in one run without
saving results to the database took
\input{build/include-full-run-duration}, with mean throughput of
\input{build/include-full-run-throughput}.  In contrast, when saving
results to the database, parsing all \numberOFlogFILES{} log files took
\input{build/include-insert-results-duration}, with mean throughput of
\input{build/include-insert-results-throughput} --- parsing takes up only
\input{build/include-skip-inserting-as-percentage-of-inserting} of
execution time when saving results to the database.

>>>>

Efficiency is an obvious concern when the parser routinely needs to parse
large log files.  The mail server that generated the \numberOFlogFILES{}
log files used in this chapter is a production mail server handling mail
for a university department; the benefit of using this mail server is that
its log files exhibit the idiosyncrasies and peculiarities that a mail
server in the wild must deal with, but the downside is that significantly
altering its Postfix configuration to accommodate this project is not an
option.  \Graphref{Mails received per day} shows the number of mails
accepted over \acronym{SMTP}, with mean and standard deviation in
\tableref{Number of mails received per day: statistics}; as expected, far
more mails are accepted on weekdays than at weekends.  Note that mail
generated on the server (e.g.\ bounce notifications, mail re-injected for
forwarding, mail sent from mailing lists) does not contribute to these
figures: in particular, the vast amounts of mail resulting from the mail
loops noticeable in later graphs are not reflected in these figures.

@@

When generating the timing data used in this section, \numberOFlogFILES{}
log files were used, each containing one day's log lines; the three months
of contiguous log files contain \numberOFlogLINEShuman{} log lines and
total \input{build/include-total-size-of-93-log-files}.  Each log file was
parsed 10 times, and the mean parsing time calculated for each log file.
The computer used for test runs was a Dell Optiplex 745, with components
shown in \tableref{Details of the computer used to generate statistics}; it
was dedicated to the task of gathering statistics from test runs, and did
not run any other programs while test runs were in progress.  Saving
results to the database was disabled for the test runs, because that
dominates the run time of the parser, and the tests are aimed at measuring
the speed of \parsername{} rather than the speed of the database and the
disks it is stored on.  Parsing all \numberOFlogFILES{} log files in one
run without saving results to the database took
\input{build/include-full-run-duration}, with mean throughput of
\input{build/include-full-run-throughput}.  In contrast, when saving
results to the database, parsing all \numberOFlogFILES{} log files took
\input{build/include-insert-results-duration}, with mean throughput of
\input{build/include-insert-results-throughput} --- parsing takes up only
\input{build/include-skip-inserting-as-percentage-of-inserting} of
execution time when saving results to the database.
